Ecosystem size and complexity as extrinsic drivers of food chain length in branching ecosystems

### 2023-03-27 rmd/manuscript.Rmd
update: ms

***Food chain length.*** At each patch and time step, we determined local FCL as the highest trophic position ($\tau_{x,t}$) of the existing species. When the predator exists, the trophic position is determined as follows:

@@

@@

We obtained the global FCL $\bar{\tau}$ for the last `r unique(df_sim$n_timestep)` time steps. We also calculated the proportion of the patch state ("No species", "B", "B + C", "B + P", and "B + C + P") to infer mechanisms that drive changes in FCL. All analysis was performed in R 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]

>>>>

***Food chain length and patch state.*** At each patch and time step, we determined local FCL as the highest trophic position ($\tau_{x,t}$) of the existing species. When the predator exists, the trophic position is determined as follows:

@@

We also calculated the proportion of the patch state ("No species", "B", "B + C", "B + P", and "B + C + P") at each time step to infer mechanisms that drive changes in FCL. The time-averaged proportion of patch state $\bar{s}$ was obtained as $\bar{s} = \frac{s_t}{N_p T}$, where $s_t$ is the number of patches in a given patch state at time step $t$.

@@

We obtained the global FCL $\bar{\tau}$ and $\bar{s}$ for the last `r unique(df_sim$n_timestep)` time steps. All analysis was performed in R 4.2.1 [@rcoreteamLanguageEnvironmentStatistical2021]
